\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-26 paper/paper.tex
Using latex rendered graph now instead of matlab graph

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}

@@

\begin{figure*}[t]
	\label{fig:error}
	\includegraphics[width=\textwidth,height=9cm]{Average_Error}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error comes from discrepancy between the tracker and the ground truth on the boundaries of the blurred tags. At around frames 30 and 200, the tracker loses the tag momentarily due to a sudden rotation but is able to recover without needing to be manually reset.}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=7cm,height=4.75cm]{RefPatches}
	\caption{The reference patches of various tags (by ID) in a multi-Tag tracking scenario.}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=7cm,height=4.75cm]{Particles2}
	\caption{The distribution of particles and their weights with respect to the X,Y position of the particles.}
\end{figure}

>>>>

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{pgfplots}

\pgfplotsset{compat=1.7}

@@

\begin{figure*}[t]
	\centering
	\label{fig:error}
	\begin{tikzpicture}[trim axis left]
	\begin{axis}[
		width=\textwidth,
		height=9cm,
		title= {Average Corner Error on the Single-Tag Sequence},
		xlabel = {Time (Frame Number)},
		ylabel = {Average Corner Error (Pixels)},
		xmin=0, xmax=250,
		ymin=0, ymax=80,
		xtick={0,50,100,150,200,250},
		ytick={0,10,20,30,40,50,60, 70}
	]
	\addplot [
		color=blue,
		mark=none,
	] table {corner_error.dat};
\end{axis}
\end{tikzpicture}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error comes from discrepancy between the tracker and the ground truth on the boundaries of the blurred tags. At around frames 30 and 200, the tracker loses the tag momentarily due to a sudden rotation but is able to recover without needing to be manually reset.}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=7cm,height=4.75cm]{RefPatches}
	\caption{The reference patches of various tags (by ID) in a multi-Tag tracking scenario.}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=8cm,height=6cm]{Particles2}
	\caption{The distribution of particles and their weights with respect to the X,Y position of the particles.}
\end{figure}
